An In-Depth Analysis of Student Prompts With CharlieBot \\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-08-01 paper/paper.tex
basic updates

\title{An In-Depth Analysis of Student Prompts Using CharlieBot \\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

@@

@@

\section{Result and Discussion}

Bellow is the distribution of the messages in the categories:

\centerline{\includegraphics[scale=0.6]{figures/figure1.png}}

@@

\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

>>>>

\title{An In-Depth Analysis of Student Prompts With CharlieBot \\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

According \cite{LO2024105100} further research about the use of AI tools in
education is needed to understand how these tools can be used to improve
students' learning experience. In particular, the study suggested that future
research on students' study habits.

@@

The paper \cite{10343037} examined students from different demographic groups
using AI tools like ChatGPT, comparing perceptions and impacts
among these groups. The results showed that AI tools had a positive impact on
academic performance, especially for students with less prior experience.

@@

\section{Results and Discussion}

The graph \ref{fig:graph1} shows the distribution of the messages in the
categories:
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.7]{figures/figure1.png}
    \caption{Classification of messages.}
    \label{fig:graph1}
\end{figure}

@@
